\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{etoolbox}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTop}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheadingTop}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------Variables-------------
\newtoggle{Finance}
\toggletrue{Finance}
%--------------------------------


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://palashtaneja.com/}{\Large Palash Taneja}} & Email : \href{mailto:tanejapalash@gmail.com}{tanejapalash@gmail.com}\\
  \href{https://ptaneja.com}{https://ptaneja.com} & Mobile : \href{tel:7378889221}{+1-737-888-9221} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingTop
      {University of Texas at Austin}{Austin, TX}
      {Bachelor of Science in Computer Science Honors;  GPA: 3.83}{Aug. 2019 -- Dec. 2022}
      \resumeSubSubheadingTop{Operating Systems Honors, Data Structures Hon., Data Mining Hon., Computer Architecture Hon.}{}
      \resumeSubSubheadingTop{Network Security Hon., Concurrency Hon., Algorithms Hon.}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bloomberg L.P.}{New York, NY}
      {Software Engineering Intern}{June 2020 - August 2020}
      \resumeItemListStart
        \resumeItem{Derivatives}
        {Worked on team doing real-time financial derivatives data analysis in Python.}
        \resumeItem{Data Science}{Built fault detection system for machine learning system using statistical methods in scikit-learn}
        \resumeItem{Backend}{Improved database queries, increasing performance for my workloads by upto {\bf 500\%}.}
        \resumeItem{Full Stack}
          {Deployed a data visualization web-app in {\bf Python (Flask)} and {\bf React}. Project led to improved employee productivity by decreasing time to get metrics by {\bf 10x}}
      \resumeItemListEnd

      \resumeSubheading
      {University of Texas at Austin}{Austin, TX}{Teaching Assistant}{Jan 2021 - Present}
      \resumeItemListStart
        \resumeItem{Operating Systems}
          {Taught {\bf C++} for systems, multithreading, synchronization, and virtual memory to 50 students. Guiding students to build an operating system kernel and GUI from scratch.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {University Computational Finance Club}{Austin, TX}
      {Director}{Spring 2020 - Present}
      \resumeItemListStart
        \resumeItem{Portfolio Management}
          {Managed a \$10k portfolio. Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine for simulating, backtesting strategies.}
        \resumeItem{WallStreetBets}
          {Pandas, React dashboard monitoring /r/WallStreetBets' topics for momentum investing}
      \resumeItemListEnd

      \resumeSubheading
      {Facebook}{Mountain View, CA}
      {Content Creator}{June 2020 - Oct 2020}
      \resumeItemListStart
        \resumeItem{Platform}
          {Helped to create content and shape an early-stage Facebook iOS app targeted to my demographic}
      \resumeItemListEnd
    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \iftoggle{Finance}{
      \resumeSubItem{CoronOS}
        {Functional Operating System kernel and GUI from scratch in {\bf C++}, managed a team of 60 peers, and worked on porting a full kernel from x86 to {\bf embedded systems} running ARM processors.}
      \resumeSubItem{Basketball bets}
      {Compiled fantasy basketball betting data from rotogrinders and trained a tree-based model to pick teams and make predictions. Made \$60k in backtests.}
      \resumeSubItem{\href{https://lovesong.dating}{LoveSong}}
      {Dating platform that matches people using a clustering machine learning algorithms based on their music taste. 500 users in 3 days. Backend in {\bf Express.js, sqlite3}; ML in {\bf scikit-learn}; deployed on {\bf AWS Lambda}.}
      \resumeSubItem{Dubit}
      {{\bf Python} and {\bf Node.js} platform that creates real-time translations of YouTube videos. {\bf \$100k grant from IBM} for making education more accessible in developing countries.}
      \resumeSubItem{Vision}
      {Improves web-interactivity for visually impaired users by adding conversational navigation to Chrome. Browser extension in {\bf JavaScript}, used Google Speech and Voice APIs}
    }{
      \resumeSubItem{CoronOS}
      {Functional Operating System kernel and GUI from scratch in {\bf C++}, managed a team of 60 peers, and worked on porting a full kernel from x86 to {\bf embedded systems} running ARM processors.}
      \resumeSubItem{\href{https://lovesong.dating}{LoveSong}}
      {Dating platform that matches people using a clustering machine learning algorithms based on their music taste. 500 users in 3 days. Backend in {\bf Express.js, sqlite3}; ML in {\bf scikit-learn}; deployed on {\bf AWS Lambda}.}
      \resumeSubItem{Dubit}
      {{\bf Python} and {\bf Node.js} platform that creates real-time translations of YouTube videos. {\bf \$100k grant from IBM} for making education more accessible in developing countries.}
      \resumeSubItem{Vision}
      {Improves web-interactivity for visually impaired users by adding conversational navigation to Chrome. Browser extension in {\bf JavaScript}, used Google Speech and Voice APIs}
      \resumeSubItem{Basketball bets}
      {Compiled fantasy basketball betting data from rotogrinders and trained a tree-based model to pick teams and make predictions. Made \$60k in backtests.}
    }

  \resumeSubHeadingListEnd

%

%--------HONORS--------------------------
\section{Honors}
  \resumeSubHeadingListStart
    \resumeSubItem{Winner}{Apple Swift Student Challenge 2020, featured on \href{https://www.apple.com/newsroom/2020/06/apples-wwdc20-swift-student-challenge-winners-determined-to-shape-the-future/}{apple.com}, presented project to CEO Tim Cook}
    \resumeSubItem{IOI}{Qualified for Indian National Olympiad in Informatics: programming contest for selecting India's IOI team}
    \resumeSubItem{Winner}{Apple World Wide Developer Conference Scholarship 2019, presented project to CEO Tim Cook}
    \resumeSubItem{Published}{Paper on detecting Parkinson's diseases using recurrent neural networks at {\bf MIT IEEE URTC}}
    \resumeSubItem{Grand Prize Winner}{Google Code-in, open-software development contest, worked on a machine learning visual IDE}
    \resumeSubItem{Winner}{Enterpreneurship summit organized by University of Melbourne and ASES, Stanford University}
  \resumeSubHeadingListEnd
%----------------------------------------


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
  \resumeSubItem{Languages}{C++, Python, Javascript, SQL, Java, Swift, Go}
  \resumeSubItem{Technologies}{AWS Lambda, React, React Native, Kubernetes, Tensorflow, PyTorch, Scikit-Learn, Pandas, Numpy}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
